Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-12-14 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
swap out figure for slanted cell figure

Cut cell grids were created by starting from a uniform grid, moving all cell vertices lying underneath the orography up to the surface.  Then, the OpenFOAM utility \texttt{snappyHexMesh} was used to remove cells whose centres lay below the surface.
In addition, the utility displaces boundary vertices so that they are `snapped' to the surface \citep{openfoam2015}.  An example of the resulting cut cell grid is shown in figure~\ref{fig:grid}c.

@@

\begin{figure*}
	\centering
	\includegraphics{../fig-snappyHexMesh/fig-snappyHexMesh.pdf}
	%
	\caption{Illustrative behaviour of the \texttt{snappyHexMesh} tool in cut cell grid creation.  The terrain surface, denoted by a thick grey line, is taken from the lower boundary of the BTF grid.   The surface is intersected with a rectangular grid shown by thin solid lines.  Vertex $v$ is `snapped' to the surface, moving from the position marked by the open circle to that of the closed circle.  The resultant cut cell grid is shown by thick dashed lines.  With a typical cut cell technique, cell $c$ would be a pentagon, as shown by the dotted line, but \texttt{snappyHexMesh} produces a quadrangular cell.}
	\label{fig:snappyHexMesh}
\end{figure*}

>>>>

\TODO{revise these three paragraphs to describe the slanted cell mesh}
Cut cell grids were created by starting from a uniform grid, moving all cell vertices lying underneath the orography up to the surface.  Then, the OpenFOAM utility \texttt{snappyHexMesh} was used to remove cells whose centres lay below the surface.
In addition, the utility displaces boundary vertices so that they are `snapped' to the surface \citep{openfoam2015}.  An example of the resulting cut cell grid is shown in figure~\ref{fig:grid}c.

@@

\begin{figure*}
	\centering
	\includegraphics{../fig-grid-generation/fig-grid-generation.pdf}
	%
	\caption{Illustration of a slanted cell grid (a) before, and (b) after construction.
	The terrain surface, denoted by a heavy dotted line, intersects a uniform rectangular grid comprising four cells, $c_1$, $c_2$, $c_3$ and $c_4$.  The cell vertices, marked by open circles, are moved upwards to the points at which the terrain intersects vertical cell edges, marked by filled circles.  Cells that have no volume are removed.  Where a cell has two vertices occupying the same point, the zero-length edge that joins those vertices is removed.  In this illustration, cell $c_4$ is removed because it has no volume, and the zero-length edge at point $p$ is removed to create a triangular cell, $c_3$.}
	\label{fig:grid-generation}
\end{figure*}
